A Poll-of-Polls Forecast for the 2024 U.S. Presidential Election: Analyzing Support Trends for Harris by Pollster and State

### 2024-11-04 paper/paper.qmd
supplementation to idealized methodology contents

The New York Times/Siena College polling partnership, the polling organization that accounted for the majority of polls in our analysis (@fig-pollster), conducts polls tailored for specific elections, such as state or national races [@nyt_siena_2020_methodology]. Their sample size typically includes 600 to 1000 likely voters per poll, with oversampling in battleground states to capture regional nuances [@nyt_siena_2020_methodology]. The methodology uses random-digit dialing (RDD) for landlines and mobile phones to ensure representative sample coverage across demographics. In addition, online surveys are administered to complement phone-based responses, ensuring broader accessibility [@nyt_siena_2020_methodology]. The stratified random sampling approach is employed, where the population is divided into strata (based on demographic variables like race, education, and geography), and a random sample is drawn from each stratum [@tellingstories]. This allows for precision in reflecting the political leanings and key demographic shifts in specific regions.

The organization intends to enhance transparency in how public opinion is assessed, ensuring that questions are carefully designed to represent contemporary political discussions, and that the terminology is polished through a process of iterative testing to achieve clarity. They devote extensive resources to cognitive testing to ensure question wording reflects what the public thinks [@siena_scri_2024_poll]. Their polling methodology stands out in that its strategic focus on using representative samples reflect political leanings and demographics of a region for more contextual and precise polling. Siena/NYT has its reputation for accurately predicting key battleground state outcomes during previous elections, such as Florida in 2016[@siena_nyt_perfect_partnership_2024].

The limitations of Siena/NYT's methodology are the challenge of polling itself. Since polling is a "snapshot in time",  the results can fluctuate based on recent political events or campaign dynamics. Additionally, there are still issues with non-response bias in polling, particularly among the hard-to-reach voter or voters suspicious of polling organizations themselves [@pew2023polling].

@@

The proposed methodology for forecasting the 2024 U.S. presidential election with a budget of $100,000 would be designed as follows. First, a stratified random sampling method will be employed that allows for the capture of the demographic elements such as age, gender, race, and education level [@pew2023polling]. We will focus on 10 battleground states including Florida, Pennsylvania, Michigan, and Arizona, each receiving a budget of $7,000. For each state, $5,000 would be allocated for telephone and online surveys, while $2,000 would be allocated for training local staff for telephone outreach and conducting data entry to maintain data quality and consistency. This targeted investment could alleviate bias and make the sample more representative of the population [@pew2023polling], enhancing the reliability and inclusiveness of the gathered data.

In addition to robust sampling, the methodology incorporates high-quality questionnaire design and testing. We would invest $15,000 in this with $5,000 on initial drafting and expert review to ensure questions are clear and unbiased. $7,000 would be spend on conducting pre-tests and pilot studeies for refinement [@driveresearch_cognitive_testing] and $3,000 would be allocated to final review and translation of the survey questions. Cognitive testing and iterative feedback loops are expected to improve the validity and accuracy of the collected data to derive reliable prediction results [@presser2004pretesting].

Then, $10,000 would be assigned for data processing and weighting. Weighting methods that account for groups that are underrepresented ensure that the outcomes are not skewed by sampling errors [@pew2023polling]. Post-stratification weighting which ensures that the sample accurately represents the U.S voting population will take up $5,000 while data cleaning and consistency checks for preventing bias from erroneous entries or duplicates will take up $5,000.

The final model would use Bayesian hierarchical modeling, which allows for more flexible modeling of uncertainty and variation across states, pollsters, and other external factors. These models, along with out-of-sample testing and cross-validation, enable accurate prediction sensitive to the dynamics of real-world changes, including political events [@pew2023polling]. By investing $3,000 on model setup and calibration and $2,000 on cross-validation and testing, we expect to ensure the model remains robust and provides reliable predictions under various electoral scenarios.

@@

The proposed survey questionnarie design is in the following link:
\
https://forms.gle/vehDvpDNDGZ8WCn47

>>>>

The New York Times/Siena College polling partnership, the polling organization that accounts for the majority of polls in our analysis (@fig-pollster), employs a methodology tailored to capture voter preferences for specific elections, whether at the state or national level [@nyt_siena_2020_methodology]. Sample sizes typically range from 600 to 1000 likely voters, with an emphasis on oversampling in battleground states to better reflect regional political dynamics [@nyt_siena_2020_methodology].

To enhance representativeness, the organization uses a mixed-mode approach that combines random-digit dialing (RDD) for landlines and mobile phones with online surveys, increasing accessibility and demographic coverage [@nyt_siena_2020_methodology]. The polling process relies on stratified random sampling, a technique where the population is divided into mutually exclusive and collectively exhaustive subgroups, or strata [@tellingstories], based on key demographic variables such as race, education, and geographic location. Within each stratum, random sampling ensures proportional representation. This approach is especially effective in capturing variation within diverse populations [@lohr2019sampling], as it controls for demographic factors that could otherwise introduce bias. However, stratified sampling can also introduce complexities, such as difficulty in defining strata boundaries, which can affect overall precision if strata are not well-chosen [@lohr2019sampling].

In addition, the Siena/NYT intends to enhance transparency and reliability through cognitive testing of survey questions. Cognitive testing allows the pollster to evaluate whether respondents interpret questions as intended, which is a necessary process in minimizing response bias and improving question clarity [@presser2004pretesting]. This iterative approach ensures that question wording resonates with respondents' current understanding of political issues, thus reduces measurement error[@siena_scri_2024_poll].

A distinctive strength of this organization's approach is its commitment to accurately reflecting the demographics and political leanings of specific regions. This kind of approach has been validated in high-profile cases, such as the accurate prediction of battleground state outcomes in the 2016 Florida election [@siena_nyt_perfect_partnership_2024]. By using robust sampling methods and iterative question refinement, their polls are well-positioned to reflect regional voter behavior with a higher degree of accuracy.

However, challenges remain in achieving a fully representative sample. Polling captures a "snapshot in time"[@tellingstories] and is vulnerable to shifts caused by recent political events, which can introduce volatility into results. Additionally, non-response bias remains an issue, as certain groups that are distrustful of polling organizations or those difficult to reach by phone are often underrepresented [@pew2023polling]. Simulation studies in the literature show that non-response bias can skew results, especially in polarized contexts, unless corrective weighting or follow-up efforts are applied [@presser2004pretesting].

By continuously refining their approach by using corrective weighting [@nyt_siena_2020_methodology], Siena/NYT intends to remain a credible source of insights into the evolving dynamics of U.S. elections. To be more specific about this weighting method, it assigns different weights to responses based on demographic factors such as age, race, gender, or geographic location [@nyt_siena_2020_methodology]. For instance, if a poll has fewer responses from young adults compared to their actual proportion in the population, each response from a young adult might be given a higher weight to compensate. This adjustment helps balance out the representation of various groups, making the poll more reflective of the overall population [@siena_nyt_perfect_partnership_2024].

@@

The proposed methodology for forecasting the 2024 U.S. presidential election with a budget of $100,000 would be designed as follows. First, a stratified random sampling method will be employed that allows for the capture of the demographic elements such as age, gender, race, and education level [@pew2023polling]. Stratified sampling involves dividing the population into mutually exclusive subgroups, or strata, based on demographic factors, then randomly sampling from each stratum [@tellingstories]. This approach allows us to control for variation within subgroups, which improves representation and reduces sampling error compared to simple random sampling. However, as noted by Lohr (2019), defining appropriate strata boundaries can be challenging and may impact the precision of estimates if not carefully managed [@lohr2019sampling]. By focusing on 10 battleground states including Florida, Pennsylvania, Michigan, and Arizona, we can capture the diverse political landscapes critical to the election outcome. Each state will receive a $7,000 budget, with $5,000 allocated to conducting telephone and online surveys and $2,000 for training local staff for outreach and data entry. This budget allocation aims to address potential sources of bias, ensuring the sample is reflective of the population and enhancing data reliability.

To further strengthen our methodology, we will invest $15,000 in questionnaire design and testing. High-quality questionnaire design is essential for minimizing response bias and ensuring that questions are clear and unbiased [@tellingstories]. With $5,000 on initial drafting and expert review, $7,000 on conducting pre-tests and pilot studies [@driveresearch_cognitive_testing] and $3,000 on final review and translation of the survey questions, we expect to improve the validity and reliability of the collected data. In particular, pre-tests, rooted in cognitive testing, is expected to help assess whether respondents interpret questions as intended, a critical step for reducing measurement error and enhancing question validity [@presser2004pretesting].

Then, $10,000 will be dedicated to data weighting and cleaning. Post-stratification weighting will adjust for demographic imbalances in the sample, helping to correct for potential biases from non-response and underrepresented groups [@valliant2019poststratification]. By assigning $5,000 for these weighting procedures, we aim to ensure that the sample aligns as accurately as possible with the U.S. voting population. Additionally, $5,000 will be allocated to data cleaning, which includes consistency checks and removal of duplicates or erroneous entries, further improving data quality and reducing bias [@pew2023polling].

Our final prediction model will employ Bayesian hierarchical modeling, which allows us to account for uncertainty and variability across states, pollsters, and external factors. Bayesian models are particularly effective in election forecasting, as they enable dynamic updates based on real-world changes, such as shifts in public opinion following political events. By allocating $3,000 for model setup and calibration and $2,000 for cross-validation and out-of-sample testing, we ensure the model’s robustness in capturing complex electoral dynamics [@pew2023polling]. This approach not only provides flexibility in handling diverse data sources but also improves predictive accuracy through structured handling of variability and uncertainty.

The final model would use Bayesian hierarchical modeling, which allows for more flexible modeling of uncertainty and variation across states, pollsters, and other external factors. These models, along with out-of-sample testing and cross-validation, enable accurate prediction sensitive to the dynamics of real-world changes, including political events [@stata2024bayesian]. By investing $3,000 on model setup and calibration and $2,000 on cross-validation and testing, we expect to ensure the model remains robust and provides reliable predictions under various electoral scenarios.

In summary, this methodology balances rigorous sampling, robust question design, and advanced statistical modeling, all underpinned by established survey and sampling principles. These practices aim to deliver a reliable and comprehensive forecast for the 2024 U.S. presidential election.

@@

The proposed survey questionnarie design is in the following link:
\
https://forms.gle/vehDvpDNDGZ8WCn47
\
Following the guidance of @tellingstories, we aimed to have survey questions that are conversational and flow from one to the next, grouped within topics [@elson2018question]. We refined the wording of questions to be based on what the respondent would be comfortable with, simultaneously checking for whether the survey questions could appropriately relate to measuring the estimand [@tellingstories].
